---
title: "inventory data cleaning and matching"
author: "Nidanur Basturk"
date: "`r Sys.Date()`"
output: html_document
---


This document provides a **generic and anonymized version** of the workflow used for creating the variable database of **The NextGen Harmonised Data Gateway Variable Database** at GESIS Leibniz Institute for the Social Sciences. This tool supports data harmonisation and can be accessed here: [NextGen Harmonised Data Gateway](https://infra4nextgen.com).

Below are the steps for data cleaning, question matching, and similarity analysis using the `harmonydata` package.

If you have questions about this script, please contact: **[nidanur.bastuerk@gesis.org]**


#Set up

## Session info

```{r}
## For replicability: session information 

session_info <- print(sessionInfo())

getwd()
```

R version 4.4.0 (2024-04-24 ucrt)
Platform: x86_64-w64-mingw32/x64
Running under: Windows 10 x64 (build 19045)




```{r setup, include=FALSE}
Sys.setenv(LANG = "en")
## clean environment
#rm(list = ls())

# Define which packages needed for analyses
p_needed <-
  c("knitr",
    "readxl",
    "writexl",
    "dplyr", 
    "stargazer",
    "ggplot2",
    "viridis",
    "rsample",
    "data.table",
    "matrixStats",
    "webshot2",
    "gt",
    "harmonydata",
    "janitor",
    "purrr",
    "text2vec")

# Check which packages are already installed on  computer
packages <- rownames(installed.packages())



# Check which packages are not installed
p_to_install <- p_needed[!(p_needed %in% packages)]

if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_needed, require, character.only = TRUE)


# Set an option for the final document that can be produced from the .Rmd file.
knitr::opts_chunk$set(echo = TRUE)


```



```{r}

# Load required packages
library(gt)
library(webshot2)
library(tidyverse)
library(readxl)
library(openxlsx)
library(haven)
library(labelled)
library(harmonydata)
library(janitor)
library(purrr)
library(dplyr)
library(stringr)
library(tidytext)
library(writexl)


```

# Data Cleaning

##Load and Inspect the Data 

```{r}


# Step 1: Load the Excel file and check the available sheet names
file_path <- "data/Inventory_30102024.xlsx"  #question text, response categories, year, survey name and so on are stored here


# Step 2: Load the selected sheet into a data frame and clean column names
inventory_data <- read_excel(file_path) %>%
  clean_names()  # Clean the column names for consistency

# Step 3: Check the structure and column names of the loaded data
colnames(inventory_data)  # View the column names
#str(inventory_data)  # Check the structure of the data




```


## Add Unique Question Identifiers

```{r}

# Group by survey_name, create the question_number column, and select specific columns
grouped_inventory_data <- inventory_data %>%
  group_by(survey_name) %>%  # Group by survey_name
  mutate(
    question_number = paste0(survey_name, "_", year, "_", row_number())  # Create the custom question number
  ) %>%
  ungroup() %>%  # Ungroup to prevent further issues
  select(
    question_number, survey_name, year, 
    item_text, response_categories_original, key  # Select only the specified columns
  )

#writexl::write_xlsx(grouped_inventory_data,"data/grouped_inventory_data.xlsx")

```



```{r}

grouped_inventory_data <- read_excel("data/grouped_inventory_data.xlsx")
View(grouped_inventory_data)

```


# Text Cleaning of Common Prefixes

```{r text cleaning}


# Common prefixes provided
common_prefixes <- c(
  "to what extent you agree or disagree with each of the following statements",
  "please tell me whether you agree completely, agree somewhat, disagree somewhat or disagree completely with each statement.",
  "could you please tell me on a scale of one to 10 how satisfied you are with each of the following items",
  "how satisfied or dissatisfied were you with",
  "how true is the following statement",
  "the past 5 years, do you think",
  "How much responsibility do you think",
  "to what extent are you in favour or against",
  "in your opinion, which of the following is",
  "which of the reasons below explains why",
  "how common, if at all, do you think",
    "about how long would it take you to",
    "about how many days in total",
    "about how many",
    "about how many hours per week",
    "about how many years of",
    "about how much time in total",
    "about how often would you say",
    "all in all how likely is it",
    "all things considered how satisfied are you",
    "although you may feel that",
    "among people you have contact with on a typical weekday",
    "a household may have different sources of income",
    "a lot of people who come to live in",
    "a variety of characteristics are listed here",
    "according to you how many of your",
  "do you have any of the following",
    "do you agree or disagree",
    "do you approve or disapprove",
    "do you have very many reasons",
    "do you think that",
    "do you think the government should",
    "during the time you were growing up",
    "generally speaking",
    "how frequently do you",
    "how frequently do you make use of",
    "how good or bad do you think",
    "how important do you think",
    "how important is it for",
    "how likely do you think",
   "how much do you agree or disagree with the following statements",
    "how much",
    "how much do you agree or disagree",
    "how much do you agree",
    "how often do you",
    "how often has each of the following happened to you",
    "how often if at all",
    "how often in the past",
    "how often would you say",
    "how satisfied or dissatisfied have you been",
    "how true do you think it is that",
    "i am going to read some things",
    "i am now going to read",
    "if you had to choose which would you say",
    "in general how often",
    "in general how reliable would you rate",
    "in general how satisfied are you with",
    "in general how would you describe",
    "in general how would you rate the quality of",
    "in the last 12 months",
    "in the last five years have you",
    "in the past 4 weeks have you felt",
    "in the past 12 months how often",
    "in your main job",
    "in your opinion about how many",
    "in your opinion",
    "in your opinion how fair or unfair",
    "in your opinion how many people",
    "listed below are various areas",
    "looking at the list below",
    "looking at this card how important is each of these things",
    "on a scale from 0 to 10",
    "over the last 12 months have you",
    "please choose one option",
    "please choose your answer",
    "please choose your response",
    "please choose your views on this scale",
    "please indicate how much",
    "please indicate to what extent",
    "please indicate whether",
    "please look at the following statements",
    "please look at the following tasks",
    "please say how much enjoyment",
    "please say how much you agree",
    "please tell me how",
    "please tell me how often",
    "please tell me to what extent",
    "please tell me whether you agree or disagree",
    "please think about the last time",
    "please think back to",
    "please tick one box",
    "please tick one box for each statement",
    "please use this card to",
    "please use this card to guide",
    "read out in reverse order and mark an answer for each",
  "there are some things that many people cannot",
    "thinking about your reasons for doing",
    "thinking about your household’s total income",
    "thinking about your usual income",
    "thinking back in what year did you",
    "thinking in general about nations",
    "thinking just of the last 3 years",
    "thinking now about politics",
    "to what extent",
    "to what extent do you agree or disagree",
    "to what extent do you feel concerned",
    "to what extent would you say",
    "using this card",
    "what do you think about",
    "which do you think is better",
    "which if any of the following do you believe in",
    "which of these do you think"
)

# Sort prefixes by length in descending order to prioritize longer matches
common_prefixes <- common_prefixes[order(nchar(common_prefixes), decreasing = TRUE)]

# Function to clean question text
clean_question_text <- function(text, prefixes) {
  # Convert to lowercase
  cleaned <- tolower(text)
  
  # Step 1: Remove each prefix, starting with the longest
  for (prefix in prefixes) {
    cleaned <- str_replace(cleaned, regex(paste0("^", prefix), ignore_case = TRUE), "")
  }
  
  # Step 2: Remove common survey formatting elements
 # cleaned <- str_remove_all(cleaned, "\\(.*?\\)")  # Remove parenthetical text
  cleaned <- str_remove_all(cleaned, "\\[.*?\\]")  # Remove bracketed text
  cleaned <- str_remove_all(cleaned, "[0-9]+\\)")  # Remove numbered bullets
 # cleaned <- str_remove_all(cleaned, "\\s*\\d+\\s*")  # Remove standalone numbers
  
  # Step 3: Remove common survey stopwords
  #survey_stop_words <- c("card", "following", "whether", "statements", "please", 
                       #  "tell", "indicate", "using", "scale", "answer", "choose",
                       #  "option", "best", "describes", "mark", "tick", "box")
  
  # Combine with standard English stop words (assuming 'stop_words' contains a list of standard stopwords)
 # stop_words_combined <- unique(c(stop_words$word, survey_stop_words))
  
  # Split into words, remove stop words, and rejoin
 # words <- str_split(cleaned, "\\s+")[[1]]
 # words <- words[!words %in% stop_words_combined]
 # cleaned <- paste(words, collapse = " ")
  
  # Clean up any remaining whitespace and punctuation
  cleaned <- str_remove_all(cleaned, "[[:punct:]]")
  cleaned <- str_squish(cleaned)
  
  return(cleaned)
}


```



```{r Apply the function}

# Apply the function to the dataframe using rowwise() for proper row-by-row processing
grouped_inventory_data <- grouped_inventory_data %>%
  rowwise() %>%
  mutate(cleaned_question_pref = clean_question_text(item_text, common_prefixes)) %>%
  ungroup()


view(grouped_inventory_data)


#writexl::write_xlsx(grouped_inventory_data, "data/grouped_inventory_data_clean.xlsx")

```

# Instrument Preparation

# Prepare  Instrument List

```{r}

# Read data 
full_data <- read_excel("data/full_data_inventory_and_suveyx_data_clean.xlsx")  # two datasets merged 

# View the cleaned column names
colnames(full_data)

```


```{r}
# Step 2: Prepare the instruments by selecting relevant columns

full_instrument <- full_data %>%
  select(question_no = question_number, question_text = cleaned_question_pref)


full_instrument <- full_instrument %>%
  mutate(question_text = as.character(question_text))  # Ensure question_text is a string


full_instrument <- full_instrument %>%
  mutate(question_no = as.character(question_no))  # Ensure question_no is a string


full_instrument <- full_instrument %>%
  filter(!is.na(question_text) & question_text != "")

full_instrument <- full_instrument %>%
  mutate(question_text = str_squish(gsub("[^[:alnum:] [:punct:]]", "", question_text)))

```


```{r}
# Define a function to prepare the full instrument in the desired format
prepare_full_instrument <- function(data, instrument_name) {
  # Create a list of questions where each question is a list with 'question_no' and 'question_text'
  questions_list <- map(
    seq_len(nrow(data)), 
    ~ list(
      question_no = data$question_no[.x],
      question_text = data$question_text[.x]
    )
  )
  
  # Return the structured list
  list(
    instrument_name = instrument_name,
    questions = questions_list
  )
}

# Prepare the full instrument
full_instrument_list <- prepare_full_instrument(full_instrument, "Full_Instrument")

# Inspect the structure of the full instrument list
str(full_instrument_list)

```


ISSUE:
We have "full_data_inventory_and_suveyx_data_clean.xlsx" each row has metadata on a single survey item. Aim is to ask *match_instruments*  function to match each item with all others and calculate the similarity score for every possible match.The output supposed to be a list of 5 lists 
                                  #[1] "instruments"  
                                  #[2] "questions"                        
                                 #[3] "matches"         
                                  #[4] "query_similarity"                 
                                 #[5]"closest_catalogue_instrument_matches" 
                                 
                                 You can run chunk {r match_instruments} the first part to see the output.


But the function fails  when I attempt to do it for *full_instrument_list*.  It gives a list of 2 lists: html, head, body with no calculation results. 


The alternative: I split the data to 5 different parts by survey code and then I did 10 pairs of matching in 10 independent code with the same function and the function works perfectly.

*Nice to have* to make it all at once as we will have more data and want to have a more durable solution.:  



```{r create instrument lists-1 }


# Step 1: Split the data by survey code (first three digits of question_no)
survey_groups <- full_instrument %>%
  mutate(survey_code = substr(question_no, 1, 3)) %>%
  group_by(survey_code) %>%
  group_split()

# Create a named list of surveys for easier access
survey_data <- set_names(survey_groups, map_chr(survey_groups, ~ unique(.$survey_code)))

str(survey_data)

```





```{r create instrument lists-2}


# Create a named list of surveys for easier access
survey_data <- set_names(survey_groups, map_chr(survey_groups, ~ unique(.$survey_code)))

# Define a function to prepare each instrument in the correct format
prepare_instrument <- function(data, instrument_name) {
  questions_list <- map(
    seq_len(nrow(data)), 
    ~ list(
      question_no = data$question_no[.x],
      question_text = data$question_text[.x]
    )
  )
  list(
    instrument_name = instrument_name,
    questions = questions_list
  )
}


# Prepare instruments for each survey in survey_data
instrument_A <- prepare_instrument(survey_data$Survey_A, "Survey_A")
instrument_B <- prepare_instrument(survey_data$Survey_B, "Survey_B")
instrument_C <- prepare_instrument(survey_data$Survey_C, "Survey_C")
instrument_D <- prepare_instrument(survey_data$Survey_D, "Survey_D")
instrument_E <- prepare_instrument(survey_data$Survey_E, "Survey_E")
instrument_F <- prepare_instrument(survey_data$Survey_F, "Survey_F")

# Store each prepared instrument in a list
instruments <- list(Survey_A = instrument_A,
                    Survey_B = instrument_B,
                    Survey_C = instrument_C,
                    Survey_D = instrument_D,
                    Survey_E = instrument_E, 
                    Survey_F = instrument_F)



```



# Match Instruments (Pairwise)

```{r match_instruments}

#This chunk is the only part where harmonydata used
# loop and mapping give errors. So we do one by one. It takes 15-20 mins to run

# Match instruments by pairs and display names of matches



# Example pair matching:
A_B_pair_matches <- match_instruments(list(instrument_A, instrument_B))
A_C_pair_matches <- match_instruments(list(instrument_A, instrument_C))

print(names(A_B_pair_matches)) # this must give:
                                   #[1] "instruments"  
                                  #[2] "questions"                        
                                 #[3] "matches"         
                                  #[4] "query_similarity"                 
                                 #[5]"closest_catalogue_instrument_matches"

# Continue similarly for other pairs

```

```{r match df all}

# List the names of all variables ending with "_pair_matches"
pair_match_list <- mget(ls(pattern = "_pair_matches$"))

# Create an output folder if it doesn't exist
output_folder <- "Match_Results"
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Loop over each pair in the list
for (pair_name in names(pair_match_list)) {
  # Access the matches and questions for the current pair
  pair_match <- pair_match_list[[pair_name]]
  matches_batch <- pair_match$matches
  questions_batch <- pair_match$questions
  
  # Initialize an empty data frame for results
  match_df <- map_df(seq_along(questions_batch), function(i) {
    question1_no <- questions_batch[[i]]$question_no
    question1_text <- questions_batch[[i]]$question_text
    
    match_scores <- matches_batch[[i]]
    
    if (length(match_scores) > 0) {
      map_df(seq_along(match_scores), function(j) {
        matched_question_no <- questions_batch[[j]]$question_no
        matched_question_text <- questions_batch[[j]]$question_text
        match_score <- match_scores[[j]]
        
        # Only include matches with absolute score >= 0.60
        abs_match_score <- abs(match_score)
        if (abs_match_score >= 0.60) {
          data.frame(
            pair_name = pair_name,
            question1_no = question1_no,
            question1_text = question1_text,
            question2_no = matched_question_no,
            question2_text = matched_question_text,
            match_score = match_score,
            abs_match_score = abs_match_score,  # New column for absolute match score
            stringsAsFactors = FALSE
          )
        } else {
          NULL
        }
      })
    } else {
      NULL
    }
  })
  
  # Filter for matches between different surveys
  match_filtered_df <- match_df %>%
    filter(substr(question1_no, 1, 3) != substr(question2_no, 1, 3))
  
  # Remove duplicates where pairs of question numbers appear in reverse
  unique_pairs_df <- match_filtered_df %>%
    rowwise() %>%
    mutate(
      question_pair = paste(sort(c(question1_no, question2_no)), collapse = "_")
    ) %>%
    ungroup() %>%
    distinct(question_pair, .keep_all = TRUE) %>%
    select(-question_pair)
  
  # Step 1: Sort by `question1_no` and descending `match_score`
  unique_pairs_df <- unique_pairs_df %>%
    arrange(question1_no, desc(match_score))
  
  # Step 2: Identify the top 3 matches for each `question1_no`
  unique_pairs_df <- unique_pairs_df %>%
    group_by(question1_no) %>%
    mutate(top_match = ifelse(row_number() <= 3, "Top 3", "")) %>%  # Mark top 3
    ungroup()
  
  # Define the output file name and save
  output_file <- file.path(output_folder, paste0(pair_name, "_Matches_60.xlsx"))
 # write_xlsx(unique_pairs_df, output_file)
  cat("Saved matches for", pair_name, "with absolute score >= 0.60 to", output_file, "\n")
}


```



```{r All Matches Consolidated}


# Define the main output folder and the subfolder for consolidated results
output_folder <- "Match_Results"
consolidated_folder <- file.path(output_folder, "All_Consolidated")

# Create the consolidated folder if it doesn't exist
if (!dir.exists(consolidated_folder)) {
  dir.create(consolidated_folder)
}

# List all Excel files in the main output folder
file_list <- list.files(path = output_folder, pattern = "*.xlsx", full.names = TRUE)

# Initialize an empty list to store each data frame
df_list <- lapply(file_list, read_excel)

# Combine all data frames into a single data frame
master_df  <- bind_rows(df_list)

# Save the merged data frame as a new Excel file in the consolidated folder
output_file <- file.path(consolidated_folder, "All_Matches_Consolidated.xlsx")
# write_xlsx(master_df , output_file)

cat("All data frames have been merged and saved as 'All_Matches_Consolidated.xlsx' in the 'All_Consolidated' folder.\n")


str(master_df)


```


```{r}

# Helper function to get matches with at least `min_surveys` distinct surveys
get_multimatch_summary <- function(threshold, min_surveys) {
  # Filter for matches with the absolute match score above the threshold
  filtered_df <- master_df %>%
    filter(abs_match_score > threshold)
  
  # Group by question1_no and summarize matching surveys and texts
  summary_df <- filtered_df %>%
    group_by(question1_no, question1_text) %>%
    summarise(
      matched_surveys = list(unique(question2_no)),  # List of unique matching question numbers
      matched_texts = list(unique(question2_text)),  # List of unique matching texts
      total_matches = n_distinct(substr(question2_no, 1, 3))  # Count distinct surveys
    ) %>%
    filter(total_matches >= min_surveys) %>%  # Filter based on minimum distinct surveys matched
    mutate(
      matched_surveys = sapply(matched_surveys, paste, collapse = ", "),
      matched_texts = sapply(matched_texts, paste, collapse = " | ")
    ) %>%
    select(question1_no, question1_text, matched_surveys, matched_texts, total_matches)
  
  return(summary_df)
}

# Generate data frames for each combination of score thresholds and minimum survey counts
matches_60_2 <- get_multimatch_summary(0.60, 2)
matches_60_3 <- get_multimatch_summary(0.60, 3)
matches_60_4 <- get_multimatch_summary(0.60, 4)

matches_70_2 <- get_multimatch_summary(0.70, 2)
matches_70_3 <- get_multimatch_summary(0.70, 3)
matches_70_4 <- get_multimatch_summary(0.70, 4)

matches_80_2 <- get_multimatch_summary(0.80, 2)
matches_80_3 <- get_multimatch_summary(0.80, 3)
matches_80_4 <- get_multimatch_summary(0.80, 4)

matches_90_2 <- get_multimatch_summary(0.90, 2)
matches_90_3 <- get_multimatch_summary(0.90, 3)
matches_90_4 <- get_multimatch_summary(0.90, 4)

matches_95_2 <- get_multimatch_summary(0.95, 2)
matches_95_3 <- get_multimatch_summary(0.95, 3)
matches_95_4 <- get_multimatch_summary(0.95, 4)

str(matches_60_2)
# Save each result to separate sheets in an Excel file
# #write_xlsx(
#   list(
#     "Matches_60_2_Surveys"  = matches_60_2 ,
#     "Matches_60_3_Surveys"   = matches_60_3 ,
#     "Matches_60_4_Surveys"    = matches_60_4 , 
#     "Matches_70_2_Surveys" = matches_70_2,
#     "Matches_70_3_Surveys" = matches_70_3,
#     "Matches_70_4_Surveys" = matches_70_4,
#     "Matches_80_2_Surveys" = matches_80_2,
#     "Matches_80_3_Surveys" = matches_80_3,
#     "Matches_80_4_Surveys" = matches_80_4,
#      "Matches_90_2_Surveys" = matches_90_2,
#     "Matches_90_3_Surveys" = matches_90_3,
#     "Matches_90_4_Surveys" = matches_90_4,
#      "Matches_95_2_Surveys" = matches_95_2,
#     "Matches_95_3_Surveys" = matches_95_3,
#     "Matches_95_4_Surveys" = matches_95_4
#   ),
#   "Match_Results/All_Consolidated/Multi_Survey_Matches_Thresholds.xlsx"
# )


cat("Saved matches with different survey thresholds to Multi_Survey_Matches_Thresholds.xlsx\n")


```



# Post Output Cleaning and Merging

##Create a Cross-tabulation

```{r}
#create a cross-tabulation of survey_name by each pillar and get the count of occurrences and totals
# Objective:
# This step creates a summary table showing how many survey items fall under each pillar (e.g., demographics, digital, equal, etc.)
# across different surveys (`survey_name`). It also calculates the total number of survey items for each survey and overall.

# Define pillars - these are the columns that categorize survey items into thematic areas
pillar_columns <- c("demographics", "digital", "equal", "green", "healthy", "strong")

# Create cross-tabulation: summarize the count of survey items for each survey and pillar
cross_table <- full_data %>%
  select(survey_name, all_of(pillar_columns)) %>%  # Select only the relevant columns: survey_name and pillar columns
  pivot_longer(cols = all_of(pillar_columns), names_to = "pillar", values_to = "count") %>%  # Reshape from wide to long format
  filter(!is.na(count)) %>%  # Remove rows with missing pillar data
  group_by(survey_name, pillar) %>%  # Group by survey_name and pillar for aggregation
  summarise(count = n(), .groups = 'drop') %>%  # Count occurrences for each survey and pillar
  pivot_wider(names_from = pillar, values_from = count, values_fill = 0) %>%  # Reshape back to wide format with one column per pillar
  rowwise() %>%  # Process each survey row individually
  mutate(survey_total = sum(c_across(all_of(pillar_columns)))) %>%  # Calculate the total count of survey items per survey
  ungroup() %>%  # Ungroup for further processing
  adorn_totals("row")  # Add a grand total for all surveys across all pillars

# Print the cross-table to review the summary
print(cross_table)

# Example Output (Simulated):
# survey_name demographics digital equal healthy strong green survey_total
#    A            3      56    55      52     50     0          216
#   B            0      18    64     158    258     9          507

# Save the cross-tabulation summary as an Excel file with the current date for traceability
file_name <- paste0("data/Survey_Pillar_CrossTabulation_", Sys.Date(), ".xlsx")

# Write the cross-table to an Excel file
write_xlsx(cross_table, path = file_name)


```


## Enrich master_df with Original Information from full_data

```{r}
# Objective:
# Enhance the `master_df` (containing pairwise matching results) by appending additional metadata from the original `full_data`.
# This provides full context for the matched questions, including details like their survey, wave, topic, and response categories. 

# Inspect input and output data structures
# Input: `full_data` - contains the original survey metadata
str(full_data)  # Columns include details like survey_name, year, item_text, pillars, etc.

# Input: `master_df` - contains the pairwise matching results
str(master_df)  # Columns include match scores, question pairs, and related data

# Enrich `master_df` with additional metadata from `full_data` for both `question1_no` and `question2_no`

# Step 1: Merge metadata for `question1_no` (first question in the pair) and add a prefix "q1_"
master_df_enriched <- master_df %>%
  left_join(full_data, by = c("question1_no" = "question_number")) %>%
  rename_with(~paste0("q1_", .), matches(names(full_data)))  # Add "q1_" prefix to merged columns

# Step 2: Merge metadata for `question2_no` (second question in the pair) and add a prefix "q2_"
master_df_enriched <- master_df_enriched %>%
  left_join(full_data, by = c("question2_no" = "question_number")) %>%
  rename_with(~paste0("q2_", .), matches(names(full_data)))  # Add "q2_" prefix to merged columns

# View the structure of the enriched dataframe
str(master_df_enriched)

# Example Columns After Enrichment:
# 1. `pair_name` - Name of the pair match (e.g., "EQLS_ESS")
# 2. `q1_question_no`, `q2_question_no` - Unique question identifiers for each question in the pair
# 3. `q1_survey_name`, `q2_survey_name` - Surveys to which the matched questions belong
# 4. `q1_topic`, `q2_topic` - Topics for each question
# 5. `q1_response_categories_combined`, `q2_response_categories_combined` - Cleaned response categories for each question
# 6. `match_score`, `abs_match_score`, `top_match` - Matching scores and ranking

# Save the enriched data for further analysis and reporting
output_file <- file.path("Match_Results/All_Consolidated/Enriched_Master_Data_All_Matches_Consolidated.xlsx")  # This filed used to manually judge matched pairs and to cluster similar items for the  variable database of each pillar. 

write_xlsx(master_df_enriched, output_file)


```

