---
title: "Harmony Walkthrough - Using Harmony to Check for Correspondence Between Items Within the Same Scale"
author: "Deanna Varley"
date: "2024-11-20"
output:
  html_document:
    df_print: paged
---

This script uses the harmonydata package to check for semantic similarity/
correspondence between different wordings of the same item from the same scale.
This can be used for situations where different wordings of the same item from 
the same scale were used across different surveys/datasets and you want to 
confirm that you can treat these differently worded versions of the same item
can be treated as though they are the same item.

First, let's install and load the R packages we'll need, set the working 
directory, then load the data file we'll be using:

```{r, warning=FALSE, message=FALSE}

#----------------------Preparation and Loading Packages-------------------------

#If necessary, uncomment and install the below packages:
#install.packages("devtools")
#devtools::install_github("harmonydata/harmony_r")
#install.packages(tidyverse)
#install.packages(dplyr)
#install.packages(tidyr)
#install.packages(knitr)
#install.packages(kableExtra)
#install.packages(flextable)
#install.packages(readxl)
#library(devtools)

#Load the required packages:
library(harmonydata)
library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(flextable)
library(readxl)

harmonydata::set_url()

#---------------------Set Working Directory, Load Data--------------------------

#Set working directory:
setwd("~/Data Harmonisation Project/Content Analysis/Harmony - For Github")

#Load data
dat1 <- read_xlsx("Survey Items.xlsx") #The xlsx file is a list of survey items.

#Add an ID column to the dataframe
dat1$id<-as.character(seq(1,nrow(dat1)))

```

Note: The data loaded contains the following columns/variables:
Name (the study/survey name),
Year (the study/survey year),
Scale (the name of the scale),
Item Number (a numeric variable indicating what item number a given item is within a given scale),
Items (a text/string variable containing the text of each item from each scale),
id (a unique identifier for each row).

Next, the code below creates a function that checks for correspondence between 
differently worded versions of the same item and then returns the mean and 
range of the cosine similarity indices for all the pairs of differently worded
versions of the same survey item.

The check_correspondence function is designed to compare differently worded 
versions of the same item across instruments to assess their similarity. It 
takes the scale name and item number as inputs, filters the data to retrieve 
the relevant items, and organizes the questions into a nested list structure. 
Using the harmony_r package, it computes similarity matches and extracts these 
as a similarity matrix, then calculates the mean and range of the similarity 
values, which are returned as the output.

```{r}

#----------------------Checking Item Correspondence-----------------------------

#Creating function that will later be used to check for correspondence between
#differently worded versions of the same item:
check_correspondence <- function(scale_name, item_number) {
  #Filter data for the given scale and item number
  nested_list <- dat1 %>%
    filter(Scale == scale_name & `Item Number` == item_number) %>%
    group_by(Name) %>%
    summarise(
      instrument_name = first(Name),
      questions = list(
        lapply(1:n(), function(i) {
          list(
            question_no = id[i],
            question_text = Items[i]
          )
        })
      ),
      .groups = 'drop'
    ) %>%
    #Convert to list of lists
    mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
    pull(nested)
  
  match <- match_instruments(nested_list) #Check for matches using harmony_r package
  
  #Extract the matrix of similarity values
  df <- data.frame(match$matches[[1]])
  for (x in 1:length(match$matches)) {
    df[x, ] <- match$matches[[x]]
  }
  
  #Compute correlation values
  matrix_df <- as.matrix(df)
  cor_values <- matrix_df[lower.tri(matrix_df, diag = FALSE)]
  
  #Calculate mean and range
  item_mean <- mean(cor_values)
  item_range <- range(cor_values)
  
  return(list(mean = item_mean, range = item_range))
}
```


Next, we create another function called process_scale. The process_scale 
function processes all items in a given scale to summarize their correspondence 
results. It takes the scale name and the total number of items in the scale as 
inputs and creates a results table to store the mean similarity and range 
(minimum and maximum) for each item. For each item in the scale, it calls the 
check_correspondence function and populates a results table, which is saved as 
a new object in the global environment for future use and is returned as the 
output.

``` {r}

#Creating function to process all items of a scale and return results in a table
#Note: This function won't work for scales that need to pull corresponding 
#items from multiple scales (e.g., the K10 as it has items that correspond to 
#K6 and K5 items).
process_scale <- function(scale_name, total_items) {
  results <- data.frame(
    Item = 1:total_items,
    Mean = NA,
    `Range (Min)` = NA,
    `Range (Max)` = NA,
    check.names = FALSE
  )
  
  for (item_number in 1:total_items) {
    res <- check_correspondence(scale_name, item_number)
    results$Mean[item_number] <- res$mean
    results$`Range (Min)`[item_number] <- res$range[1]
    results$`Range (Max)`[item_number] <- res$range[2]
  }
  
  #Construct the object name by concatenating scale_name and "_results"
  object_name <- paste0(scale_name, "_results")
  
  #Assign the results data frame to an object in the environment
  assign(object_name, results, envir = .GlobalEnv)
  
  return(results)
}
```

Next, the code below defines a list of scales and the number of items they 
contain and then loops over each scale in the list to process them systematically. 
For each scale, the code extracts the scale name and item count and calls the 
process_scale function to evaluate all items in that scale. The results for each 
scale are saved as separate objects in the global environment, named based on 
the scale, such as GHQ-12_results or SDQ_results. The code then creates neatly
formatted tables.

``` {r}

#The code below creates a list of scales and their item counts (i.e., the number
#of items in each scale), then creates a loop that runs the 'process_scale'
#function for each scale in the list.

#Define the scales and their item counts (i.e., the number of items in each scale):
#Note that the list doesn't include scales that have multiple versions 
#(e.g., K10, K6 and K5) as these require different code to pull items from 
#multiple scales. These are coded separately below in separate code chunks.
scales <- list(
  "GHQ-12" = 12, 
  "SDQ" = 25,
  "CES-D" = 20,
  "GADS" = 9 
)

#Loop over each scale in the scales list:
for (scale_name in names(scales)) {
  total_items <- scales[[scale_name]]  #Get the number of items for the scale
  process_scale(scale_name, total_items)  #Call the function for each scale
}


#Create and display the results as tables:
set_flextable_defaults(
  font.family = "Times New Roman", font.size = 12, 
  border.color = "black", big.mark = "", border.width = .5)

table1 <- flextable(`GHQ-12_results`) %>% 
  bold(part = "header") %>% autofit() %>%
  set_table_properties(width = 1.0, layout = "autofit") %>%
  set_caption(caption = "Mean and Range of Item Correspondence Values for the GHQ-12")
table1

table2 <- flextable(`SDQ_results`) %>% 
  bold(part = "header") %>% autofit() %>%
  set_table_properties(width = 1.0, layout = "autofit") %>%
  set_caption(caption = "Mean and Range of Item Correspondence Values for the SDQ")
table2

table3 <- flextable(`CES-D_results`) %>% 
  bold(part = "header") %>% autofit() %>%
  set_table_properties(width = 1.0, layout = "autofit") %>%
  set_caption(caption = "Mean and Range of Item Correspondence Values for the CES-D")
table3

table4 <- flextable(`GADS_results`) %>% 
  bold(part = "header") %>% autofit() %>%
  set_table_properties(width = 1.0, layout = "autofit") %>%
  set_caption(caption = "Mean and Range of Item Correspondence Values for the GADS")
table4
```

Now, the code below shows how you can adapt the methods used above to check item 
correspondence in instances where there are multiple similar versions of a scale, 
or different scales that have identical or very similarly worded items. 
For example, the K10, K6, and K5 instruments are three very similar variations
of the K10 scale.
The code below checks for correspondence between the various versions of each 
item from the K10, along with the corresponding items from the K6 and K5 (i.e.,
item 1 from the K6 is typically identical or nearly identical to item 2 from the 
K10). As above, the code below calculates the mean, minimum, and maximum 
similarity values for each item. This code begins by creating an empty results 
dataframe (K10_results) to store these values for all 10 K10 items (as well as
the corresponding K6 and K5 items). For each item, a nested list of questions 
and their corresponding instrument names is generated using filtering and 
grouping operations on our dataframe (dat1). The match_instruments() function 
then identifies matches between items, and the results are stored in a dataframe
and matrix. The mean and range of the resulting values are then summarized 
and stored in the results dataframe (K10_results). The code then creates a 
neatly formatted table to display the results.

```{r}

#-------------Checking Item Correspondence for K10, K6 and K5-------------------

#The below code chunk will check the item correspondence for the K10 items,
#along with corresponding items from the K6 and the K5. 

#Creating an empty dataframe that will later be used to store the results:
K10_results <- data.frame(
    Item = 1:10,
    Mean = NA,
    `Range (Min)` = NA,
    `Range (Max)` = NA,
    check.names = FALSE
  )

#Checking item correspondence for K10 item 1:
#First create a nested list of all K10 item 1 items:
nested_list_k101 <- dat1 %>%
  filter(Scale=="K10" & `Item Number`==1) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  # Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  # Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k101)


df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[1,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[1,"Range (Min)"] <- range[1]
K10_results[1,"Range (Max)"] <- range[2]

#K10 item 2
nested_list_k102 <- dat1 %>%
  filter((Scale=="K10" & `Item Number`==2) | (Scale=="K6" & `Item Number`==1) | (Scale=="K5" & `Item Number`==1)) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  # Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  # Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k102)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[2,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[2,"Range (Min)"] <- range[1]
K10_results[2,"Range (Max)"] <- range[2]

#K10 item 3
nested_list_k103 <- dat1 %>%
  filter(Scale=="K10" & `Item Number`==3) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  #Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  #Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k103)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[3,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[3,"Range (Min)"] <- range[1]
K10_results[3,"Range (Max)"] <- range[2]

#K10 item 4
nested_list_k104 <- dat1 %>%
  filter((Scale=="K10" & `Item Number`==4) | (Scale=="K6" & `Item Number`==2) | (Scale=="K5" & `Item Number`==2)) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  # Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  # Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k104)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[4,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[4,"Range (Min)"] <- range[1]
K10_results[4,"Range (Max)"] <- range[2]

#K10 item 5
nested_list_k105 <- dat1 %>%
  filter((Scale=="K10" & `Item Number`==5) | (Scale=="K6" & `Item Number`==3) | (Scale=="K5" & `Item Number`==3)) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  # Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  # Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k105)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[5,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[5,"Range (Min)"] <- range[1]
K10_results[5,"Range (Max)"] <- range[2]

#K10 item 6
nested_list_k106 <- dat1 %>%
  filter(Scale=="K10" & `Item Number`==6) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  # Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  # Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k106)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[6,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[6,"Range (Min)"] <- range[1]
K10_results[6,"Range (Max)"] <- range[2]

#Nested list of just the Kessler 10 item 7
nested_list_k107 <- dat1 %>%
  filter(Scale=="K10" & `Item Number`==7) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  # Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  #Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k107)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[7,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[7,"Range (Min)"] <- range[1]
K10_results[7,"Range (Max)"] <- range[2]

#K10 item 8
nested_list_k108 <- dat1 %>%
  filter((Scale=="K10" & `Item Number`==8) | (Scale=="K6" & `Item Number`==4) | (Scale=="K5" & `Item Number`==4)) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  #Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  #Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)

match = match_instruments(nested_list_k108)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[8,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[8,"Range (Min)"] <- range[1]
K10_results[8,"Range (Max)"] <- range[2]

#K10 Item 9
nested_list_k109 <- dat1 %>%
  filter((Scale=="K10" & `Item Number`==9) | (Scale=="K6" & `Item Number`==5) | (Scale=="K5" & `Item Number`==5)) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  #Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  #Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)


match = match_instruments(nested_list_k109)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[9,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[9,"Range (Min)"] <- range[1]
K10_results[9,"Range (Max)"] <- range[2]

#K10 item 10
nested_list_k1010 <- dat1 %>%
  filter((Scale=="K10" & `Item Number`==10) | (Scale=="K6" & `Item Number`==6)) %>%
  group_by(Name) %>%
  summarise(
    instrument_name = first(Name),  #Get the study name as instrument_name
    questions = list(
      lapply(1:n(), function(i) {
        list(
          question_no = id[i],
          question_text = Items[i]
        )
      })
    ),
    .groups = 'drop'
  ) %>%
  #Convert to list of lists
  mutate(nested = map2(instrument_name, questions, ~ list(instrument_name = .x, questions = .y))) %>%
  pull(nested)

match = match_instruments(nested_list_k1010)

df <- data.frame(match$matches[[1]])
for (x in 1:length(match$matches)) {
  df[x, ] = match$matches[[x]]
}
colnames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )
rownames(df) <- lapply(match$questions, function(x) paste(x$question_no,  x$question_text , sep=" ") )

matrix_df <-as.matrix(df)
cor_values<-matrix_df[lower.tri(matrix_df, diag=FALSE)]
K10_results[10,"Mean"] <- mean(cor_values)
range<-range(cor_values)
K10_results[10,"Range (Min)"] <- range[1]
K10_results[10,"Range (Max)"] <- range[2]

#Create and display the results as a table:
set_flextable_defaults(
  font.family = "Times New Roman", font.size = 12, 
  border.color = "black", big.mark = "", border.width = .5)

table5 <- flextable(`K10_results`) %>% 
  bold(part = "header") %>% autofit() %>%
  set_table_properties(width = 1.0, layout = "autofit") %>%
  set_caption(caption = "Mean and Range of Item Correspondence Values for the K10, K6 and K5")
table5
```
